Create Figures and Tables

### 2023-11-08 Codes/2_figures_tables.rmd
generic manuscript.rnw created include both main and appendix

# Summary statistics

## Boxplot of water deficit by year

@@

## Saturated Thickness Map

@@

# Yield response to water deficit by saturated thickness level (intensive margin)

cowplot::ggsave2("Results/Figures/g_yield_intensive.pdf", g_yield_response, width = 6, height = 6)

#++++++++++++++++++++++++++++++++++++
#+ With confidence interval (seprately)
#++++++++++++++++++++++++++++++++++++
g_yield_with_conf <-
  plot_yield_data %>%
  dplyr::mutate(plot_data = list(
    plot_data[, `:=`(
      lower = y_hat - 1.96 * y_hat_se_modeled,
      upper = y_hat + 1.96 * y_hat_se_modeled
    )]
  )) %>%
  dplyr::mutate(g_fig = list(
    ggplot(plot_data) +
      geom_ribbon(
        aes(
          ymin = lower,
          ymax = upper,
          x = balance
        ),
        alpha = 0.3
      ) +
      geom_line(aes(
        y = y_hat,
        x = balance
      )) +
      facet_wrap(~sat_cat_text, ncol = 2) +
      scale_x_continuous(
        name = "Water Deficit (mm)",
        breaks = (-1:5) * 200
      ) +
      scale_y_continuous(
        name = "Yield (tonne/ha)",
        breaks = 0:14
      ) +
      theme_fig +
      theme(
        legend.position = "bottom",
        strip.background = element_blank()
      )
  )) %>%
  dplyr::select(crop, g_fig) %>%
  data.table()

ggsave("Results/Figures/g_yield_with_conf_corn.pdf", g_yield_with_conf[crop == "corn", g_fig][[1]], width = 6, height = 3.5)
ggsave("Results/Figures/g_yield_with_conf_soy.pdf", g_yield_with_conf[crop == "soy", g_fig][[1]], width = 6, height = 3.5)
```

# The impact of saturated thickness on the share of irrigated production

# Difference in the share of irrigated production (from 100)

ggsave(
  file = "Results/Figures/g_share_dif.pdf",
  g_share_dif,
  height = 4,
  width = 6
)
```

# Total impact of a decline in saturated thickness on average yield

# Test the significance of the difference in irrigated yield between the aquifer thickness categories

# Testing of the significance of yield difference (average total impact)

# The impact of water deficit on average yield by aquifer thickness category with confidence interval

@@

ggsave("Results/Figures/g_avg_yield.pdf", g_ay_response, width = 6, height = 3.5)
```

>>>>

# Figure 1: Yield response to water deficit by saturated thickness level (intensive margin)

cowplot::ggsave2("Results/Figures/g_yield_intensive.pdf", g_yield_response, width = 6, height = 6)
```

# Figure 2: Test the significance of the difference in irrigated yield between the aquifer thickness categories

# Figure 3: The impact of saturated thickness on the share of irrigated production

# Figure 4: Total impact of a decline in saturated thickness on average yield

# Figure 5: Testing of the significance of yield difference (average total impact)

# Water deficit by year (Figure 6)

@@

# Saturated Thickness Map (Figure 7)

@@

# Supplementary Information

## Figure S.1 and S.2 
```{r}
g_yield_with_conf <-
  plot_yield_data %>%
  dplyr::mutate(plot_data = list(
    plot_data[, `:=`(
      lower = y_hat - 1.96 * y_hat_se_modeled,
      upper = y_hat + 1.96 * y_hat_se_modeled
    )]
  )) %>%
  dplyr::mutate(g_fig = list(
    ggplot(plot_data) +
      geom_ribbon(
        aes(
          ymin = lower,
          ymax = upper,
          x = balance
        ),
        alpha = 0.3
      ) +
      geom_line(aes(
        y = y_hat,
        x = balance
      )) +
      facet_wrap(~sat_cat_text, ncol = 2) +
      scale_x_continuous(
        name = "Water Deficit (mm)",
        breaks = (-1:5) * 200
      ) +
      scale_y_continuous(
        name = "Yield (tonne/ha)",
        breaks = 0:14
      ) +
      theme_fig +
      theme(
        legend.position = "bottom",
        strip.background = element_blank()
      )
  )) %>%
  dplyr::select(crop, g_fig) %>%
  data.table()

ggsave("Results/Figures/g_yield_with_conf_corn.pdf", g_yield_with_conf[crop == "corn", g_fig][[1]], width = 5, height = 3.5)
ggsave("Results/Figures/g_yield_with_conf_soy.pdf", g_yield_with_conf[crop == "soy", g_fig][[1]], width = 5, height = 3.5)
```

## Figure S.3: The impact of water deficit on average yield by aquifer thickness category with confidence interval

@@

ggsave("Results/Figures/g_avg_yield.pdf", g_ay_response, width = 5, height = 4)
```

# Figure S.4: Difference in the share of irrigated production (from 100)

ggsave(
  file = "Results/Figures/g_share_dif.pdf",
  g_share_dif,
  height = 4,
  width = 5
)
```
